BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-30 Paper/D5.5/D5.5.tex
add details about GPUTrace

@@

Hence, the verification and validation of the new port can be
narrowed down to asserting that both codes apply the same operations
on the GPU. And the debugging part will consist in understanding what
diverges. To that purpose, we developed \code{GPUTrace}, inspired by
\code{strace} and \code{ltrace} tools: \code{GPUTrace} dynamically
preloads a library between the application and the GPU library, and
collects the function name, execution range and argument values (input
\emph{and} output) of the relevant function calls. These information
are traced in a unified format for all the APIs.

%
% HSG Question: why GPUTrace has to be state-full?
%
However, in contrast with \code{strace} and \code{ltrace},
\code{GPUTrace} has to be \emph{state-full}. Indeed, most of API
parameters are handles to opaque types, so, in order to provide
meaningful information, \code{GPUTrace} stores information about these
objects (handle value, buffer creation size and attributes, kernel
name and prototype, \etc{}). This is a custom trace format.

>>>>

\lstdefinestyle{customgputrace}{
  language=C,
  basicstyle=\scriptsize,
  backgroundcolor=\color{white},
  frame=single,
  captionpos=b,
  morekeywords={New, kernel, buffer, Mb, READ_WRITE, Buffer, written,
    b, at, out}
}

@@

Hence, the verification and validation of the new port can be
narrowed down to asserting that both codes apply the same operations
on the GPU. And the debugging part will consist in understanding what
diverges. To that purpose, we developed \code{GPUTrace}, inspired by
\code{strace} and \code{ltrace} tools: \code{GPUTrace} dynamically
preloads a library between the application and the GPU library, and
collects the function name, execution range and argument values (input
\emph{and} output) of the relevant function calls. These information
are traced in a unified format for all the APIs. This is a custom
trace format. Listing~\ref{lst:GPUTrace} presents a sample output
generated during \Specfem tracing.

However, in contrast with \code{strace} and \code{ltrace},
\code{GPUTrace} has to be \emph{state-full}. Indeed, most of API
parameters are handles to opaque types. So, in order to generate
meaningful traces, \code{GPUTrace} gathers information about these
objects at creation time (handle value, buffer creation size and
attributes, kernel name and prototype, \etc{}) and re-injects this
information when the objects used. A state-less implementation of
\code{GPUTrace} would highly rely on the GPU libraries introspection
capabilities, which seem not possible at the moment.

\lstset{style=customgputrace,
        caption={GPUTrace sample trace}, 
        label={lst:GPUTrace},
        numbers=left}
\begin{lstlisting}
New kernel: update_potential_kernel
...
New buffer #94, 2Mb, READ_WRITE (0x74d0420)
New buffer #95, 2Mb, READ_WRITE (0x74d08d0)
New buffer #96, 2Mb, READ_WRITE (0x74d0d80)
...
Buffer #94 written, 2314764b at +0b 
Buffer #95 written, 2314764b at +0b
Buffer #96 written, 2314764b at +0b
...
update_disp_veloc_kernel<128,1><4522,1>(
     float *displ=<buffer #94 1.00e-24, 1.00e-24, 1.00e-24, 1.00e-24, ...>
     float *veloc=<buffer #95 0.00e+00, 0.00e+00, 0.00e+00, 0.00e+00, ...>
     float *accel=<buffer #96 0.00e+00, 0.00e+00, 0.00e+00, 0.00e+00, ...>
     const int size=<578691>
     const float deltat=<1.365914e-04>
     const float deltatsqover2=<9.328606e-09>
     const float deltatover2=<6.829570e-05>
     ----
     <out> float *displ=<buffer #94 1.000e-24, 1.00e-24, 1.00e-24, 1.00e-24, ...>
     <out> float *veloc=<buffer #95 0.000e+00, 0.00e+00, 0.00e+00, 0.00e+00, ...>
     <out> float *accel=<buffer #96 0.000e+00, 0.00e+00, 0.00e+00, 0.00e+00, ...>
);
\end{lstlisting}
